Modal type theory based on the intuitionistic epistemic logic

### 2018-01-13 article.tex
added details

  \begin{prooftree}
    \AxiomC{$\Gamma \vdash \vec{x} : {\bf K} \vec{A}$}
    \AxiomC{$\vec{y} : \vec{A} \vdash M : B$}
    \BinaryInfC{$\Gamma \vdash {\bf let \:\: pure} \:\: \vec{y} = \vec{x} \:\: {\bf in} \:\: M : {\bf K} B$}
  \end{prooftree}
    \end{flushright}
  \end{minipage}
  \end{defin}

@@

  7) $FV(M \star N) = FV(M) \cup FV(N)$.
  \end{defin}

@@

  7) $(M \star N) [x := P] = (M [x := P]) \star (N [x := P])$.
  \end{defin}

@@

  1) ${\bf pure \: } (\lambda x. x) \star M \rightarrow_{\beta} M$;

  2) ${\bf pure \: } (\lambda f g x. f (g x)) \star M \star N \star P \rightarrow_{\beta} M \star (N \star
  P)$;

  3) $({\bf pure \: } M) \star (\text{pure } N) \rightarrow_{\beta} \text{pure } (M N)$;

  4) $M \star {\bf pure \: } N \rightarrow_{\beta} (\lambda f. f N) \star M$;

  5) $M_1 \rightarrow_{\beta} M_2 \Leftrightarrow {\bf pure \: } \: M_1 \rightarrow_{\beta} {\bf pure \: } \: M_2$;

  6) $M_1 \rightarrow_{\beta} M_2 \Rightarrow M_1 \star N \rightarrow_{\beta} M_2 \star N$;

  7) $N_1 \rightarrow_{\beta} N_2 \Rightarrow M \star N_1 \rightarrow_{\beta} M \star N_2$;
  \end{defin}

  In Haskell any implementation of the Applicative instance should preserve the laws proposed by McBride and
  Paterson \cite{McP}. We preserve these laws by the introduction of corresponding reduction rules (rules
  (1)-(4)). These rules will be called respectively identity rule, composition rule, homomorphism rule and
  interchange rule.

  Rules (5)-(7) are would be useful for strong normalization proof.

@@

  2) $\Gamma \vdash M \star N : \textbf{K}\beta$ implies that $\Gamma \vdash M : \textbf{K}(\alpha \to \beta)$ and
  $\Gamma \vdash N : \textbf{K}\alpha$.
  \end{lemma}

@@

  Simple induction on the derivation of $\Gamma \vdash {\bf pure \: } M : \textbf{K}\alpha$ and $\Gamma \vdash M \star N : \textbf{K}(\alpha \to \beta)$ respectively.
  \end{proof}

>>>>

  \begin{prooftree}
    \AxiomC{$\Gamma \vdash \vec{M} : {\bf K} \vec{A}$}
    \AxiomC{$\vec{N} : \vec{A} \vdash M : B$}
    \BinaryInfC{$\Gamma \vdash {\bf let \:\: pure} \:\: \vec{N} = \vec{M} \:\: {\bf in} \:\: M : {\bf K} B$}
  \end{prooftree}
    \end{flushright}
  \end{minipage}
  \end{defin}

@@

  7) $FV({\bf let \:\: pure} \:\: \vec{N} = \vec{M} \:\: {\bf in} \:\: M) = \bigcup \limits_{i = 1}^n FV(M), \text{where $n = |\vec{M}|$}$.
  \end{defin}

@@

  7) $({\bf let \:\: pure} \:\: \vec{N} = \vec{M} \:\: {\bf in} \:\: M) [x := P] = {\bf let \:\: pure} \:\: \vec{N} = (\vec{M} [x := P]) \:\: {\bf in} \:\: M$.
  \end{defin}

@@

@@

  2) $\Gamma \vdash {\bf let \: pure} \: \vec{N} = \vec{M} \: {\bf in} \: M : {\bf K} B$ implies that $\Gamma \vdash \vec{M} : {\bf K} \vec{A}$ and
$\vec{N} : \vec{A} \vdash M : B$.
  \end{lemma}

@@

Induction on the derivation of $\Gamma \vdash {\bf pure \: } M : \textbf{K}\alpha$ and $\Gamma \vdash {\bf let \: pure} \: \vec{N} = \vec{M} \: {\bf in} \: M : {\bf K} B$ respectively.
  \end{proof}
